\bf Title here

### 2020-08-20 paper/paper.Rmd
example plots of interpolation

The idea of generalised framework for diagnostic plots is inspired by the concept of grammar of graphic [@wickham2010layered], which powers the primary graphical system in R, ggplot2 [@ggplot2]. In grammar of graphic, plots are not defined by its appearance (i.e. boxplot, histogram, scatter plot etc) but by "stacked layers". Using this design, ggplot does not have to develop a gazillion of functions that each produces a different type of plot from a different data structure. Instead, it aesthetically maps variables (and its statistical transformation) in a dataset to different geometric objects (points, lines, box-and-whisker etc) and builds the plot through overlaying different layers.

@@

```{r toy-search, fig.height=5.5, fig.cap="\\label{toy-search}A comparison of plotting the same search points with different plot designs. In upper plot, points from the last three iterations span the vast majority of the plotting space leaving the first few iterations being squeezed together whilst the lower plot spaces each iteration evenly and presents summary information easy to read."}

@@

p2 <- dt %>% ggplot() + 
  geom_point(aes(x = id, y = index_val, col = as.factor(tries))) + 
  theme(legend.position = "none")

p2 / p1

@@

Figure \ref{toy-interp} shows the plot of interpolating points and it shows the algorithm starts from around 0.8 and with interpolation, gradually reaches over 0.95.

```{r toy-interp, fig.height = 3, fig.cap = "\\label{toy-interp} This is a toy example of plotting interpolated points"}
interp <- holes_2d_better_max_tries %>% 
  filter(info == "interpolation") %>% 
  mutate(id = row_number())

interp %>% 
  ggplot(aes(x = id, y = index_val, col = as.factor(tries))) + 
  geom_point() + 
  geom_line() + 
  theme(legend.position = "bottom")
```

>>>>

With a constructed data object, the construction of diagnostic plots is inspired by the concept of grammar of graphic [@wickham2010layered], which powers the primary graphical system in R, ggplot2 [@ggplot2]. In grammar of graphic, plots are not defined by its appearance (i.e. boxplot, histogram, scatter plot etc) but by "stacked layers". Using this design, ggplot does not have to develop a gazillion of functions that each produces a different type of plot from a different data structure. Instead, it aesthetically maps variables (and its statistical transformation) in a dataset to different geometric objects (points, lines, box-and-whisker etc) and builds the plot through overlaying different layers.

@@

```{r toy-search, fig.height=3, fig.cap="\\label{toy-search}A comparison of plotting the same search points with different plot designs. In upper plot, points from the last three iterations span the vast majority of the plotting space leaving the first few iterations being squeezed together whilst the lower plot spaces each iteration evenly and presents summary information easy to read."}

@@

p1

@@

Figure \ref{toy-interp} presents the interpolation of three different tour paths. The upper plot shows a desirable interpolating in each iteration with the index value being progressively and monotonically increasing.  While in the middle plot, the increases towards the target basis is not monotonical in the last two iterations and interpolated basis with higher index value can be found on the tour path. The lower plot is constructed using `search_better_random`, where a basis with smaller index value  has a probabilistic chance of being accepted and we can observe a much more involved pattern. In iteration three, the probablistic acceptance produces a monotonically decreasing interpolation whilst in iteration five, six and seven, with also a probablistic acceptance, the interpolation is now non-monotical. When the target basis has a higher index value, iteration eight reaches this basis by first decreases the index value. While the interpolation plot shows different possibilities of the change in index value on the tour path, the diagnose of the validity of each pattern and the related optimisation algorithms will be postponed to Section \ref{application}.

```{r toy-interp, fig.height = 8, fig.cap = "\\label{toy-interp} This is a toy example of plotting interpolated points"}
interp <- holes_2d_better_max_tries %>% 
  filter(info == "interpolation") %>% 
  mutate(id = row_number())

p1 <- interp %>% 
  ggplot(aes(x = id, y = index_val, col = as.factor(tries))) + 
  geom_point() + 
  geom_line() + 
  theme(legend.position = "bottom")

p2 <- interrupt_no %>% explore_trace_interp() + 
  theme(legend.position = "bottom")

p3 <- holes_2d_better_random %>% explore_trace_interp() + 
  theme(legend.position = "bottom")

p1 / p2 / p3
```

### 2020-08-20 paper/paper.tex
example plots of interpolation

The idea of generalised framework for diagnostic plots is inspired by
the concept of grammar of graphic \citep{wickham2010layered}, which
powers the primary graphical system in R, ggplot2 \citep{ggplot2}. In
grammar of graphic, plots are not defined by its appearance
(i.e.~boxplot, histogram, scatter plot etc) but by ``stacked layers''.
Using this design, ggplot does not have to develop a gazillion of
functions that each produces a different type of plot from a different
data structure. Instead, it aesthetically maps variables (and its
statistical transformation) in a dataset to different geometric objects
(points, lines, box-and-whisker etc) and builds the plot through
overlaying different layers.

@@

Figure \ref{toy-interp} shows the plot of interpolating points and it
shows the algorithm starts from around 0.8 and with interpolation,
gradually reaches over 0.95.

>>>>

With a constructed data object, the construction of diagnostic plots is
inspired by the concept of grammar of graphic
\citep{wickham2010layered}, which powers the primary graphical system in
R, ggplot2 \citep{ggplot2}. In grammar of graphic, plots are not defined
by its appearance (i.e.~boxplot, histogram, scatter plot etc) but by
``stacked layers''. Using this design, ggplot does not have to develop a
gazillion of functions that each produces a different type of plot from
a different data structure. Instead, it aesthetically maps variables
(and its statistical transformation) in a dataset to different geometric
objects (points, lines, box-and-whisker etc) and builds the plot through
overlaying different layers.

@@

Figure \ref{toy-interp} presents the interpolation of three different
tour paths. The upper plot shows a desirable interpolating in each
iteration with the index value being progressively and monotonically
increasing. While in the middle plot, the increases towards the target
basis is not monotonical in the last two iterations and interpolated
basis with higher index value can be found on the tour path. The lower
plot is constructed using \texttt{search\_better\_random}, where a basis
with smaller index value has a probabilistic chance of being accepted
and we can observe a much more involved pattern. In iteration three, the
probablistic acceptance produces a monotonically decreasing
interpolation whilst in iteration five, six and seven, with also a
probablistic acceptance, the interpolation is now non-monotical. When
the target basis has a higher index value, iteration eight reaches this
basis by first decreases the index value. While the interpolation plot
shows different possibilities of the change in index value on the tour
path, the diagnose of the validity of each pattern and the related
optimisation algorithms will be postponed to Section \ref{application}.
